Wireless Automobile Detection, License Plate Processing, and Data Availability Network

### 2014-04-30 paper/paper.tex
Fixed figure

\subsection{Introduction}

The parking lots at the Colorado School of Mines (CSM) can be a source of frustration for students and faculty members. Because space on campus is limited, the lots are often unable to accommodate everyone who needs to use them. Students need to choose a lot before they go to class; however, knowing which lots have free spaces usually requires driving through the lots looking for a space. The extra time spent searching one or many lots can make students or faculty late for class. If campus members could find out which lots had available spaces before they arrived, much time and frustration could be saved. The goal of this project is to design and deploy a working parking lot monitoring system that will be the first step towards a better parking experience on the CSM campus. The system will keep track of both the number of vehicles in a parking lot and the license plate numbers of those vehicles. The information will be available online to system administrators and CSM campus members. There are two main parts to this project:

@@

\subsection{Related Work}
The ACMx group at CSM has designed a system named SmartLots to track the number of vehicles in a parking lot. Their system is a wireless sensor network consisting of sensor nodes and a central base station. The sensor nodes are based on the Arduino Fio microcontroller platform equipped with triaxial magnetometers and XBee Pro radios. The base station will be a Raspberry Pi connected to the internet via ethernet. The information collected by the sensor nodes is transmitted to the base station and forwarded to a server running a small web application. The system is described in \cite{stillwell2013} and \cite{parkingWiki}. \cite{stillwell2013} describes an implementation of a system to detect automobiles entering and exiting a parking lot using the Arduino Fio and the Raspberry Pi. This system uses the IEEE 802.15.4 communications standard to communicate automobile detection data from the sensor nodes to the base station. \cite{parkingWiki} describes the ongoing status of the ACMx project. At the time of writing this proposal, the ACMx team has created a website that will display the status of the CTLM upper and lower lots once the monitoring system has been deployed. \cite{parkingWiki} is updated periodically with new information about project progress. The project described in this proposal will augment and extend the ACMx project while collaborating closely with Stillwell (ACMx president and author of \cite{stillwell2013}), with the goal of a real world deployment by May 2014.

\section{Proposed Work}
\subsection{Overview}
The project we are proposing will be an extension of the ACMx SmartLots project. We will collaborate closely with Stillwell and the ACMx group to create and deploy the first working parking lot monitoring system on the CSM campus. Our system will consist of several components, each of which will be either an extension of a current SmartLots system or an entirely new subsystem that will be integrated into the existing system. Figure \ref{fig:system} shows the overall architecture of our system.

@@

\subsection{Automobile Detection}
The automobile detection subsystem will provide a means for detecting ingress and egress of vehicles from a parking lot. This subsystem is to be placed on the side of the road next to each parking lot entrance and exit. Automobiles will be detected using a magnetometer which perceives the induced change in the local magnetic field as the metallic structure of the vehicle passes by, as described in \cite{stillwell2013}. The automobile detection subsystem will be based around the commercially available Arduino Fio 16-bit  platform which utilizes the ubiquitous Atmel ATMEGA328p microcontroller. When an automobile is detected by the Arduino Fio, a packet will be sent through the onboard XBee Pro radio to the central base station (described in section 2.4). The packet will  contain the direction of the passing vehicle. At the time of detection, a hardware interrupt will also be sent to the license plate recognition system to awaken it from sleep mode.

@@

\subsubsection{Tests and Analyses}
Because the ACMx group has already written the necessary software and designed a working configuration for detecting vehicles with the Arduino Fios, the bulk of our work on the automobile detection subsystem will involve a variety of tests and analyses to ensure system and data integrity. Power consumption analyses will be conducted on the automobile detection and license plate image acquisition subsystem to identify power usage per main component (Figure~\ref{fig:autodetect}) while the mote is in different states, such as sleeping and detecting vehicles. Such an analysis will allow us to allocate how much time the mote is allowed to spend in each state and determine the required lithium polymer battery capacity.

@@

\subsection{License Plate Image Acquisition}
Once the Acquisition Raspberry Pi receives the interrupt from the vehicle detection Arduino Fio, it will begin the process of obtaining a picture of the vehicle's license plate. This procedure will be separated into two separate sections: image acquisition and license plate detection.

\subsubsection{Image Acquisition}
While the automobile detection subsystem correctly identifies when a vehicle enters the lot, the image acquisition subsystem will be responsible for determining when to capture a picture of that car in order to optimize the quality of the license plate image. The timing difference between when the Raspberry Pi receives the interrupt and when it actually captures the picture will initially be determined experimentally using the average speed at which cars enter the parking lot. As the project progresses, this timing will be fine-tuned in order to capture the optimal image every time. The goal of this subsystem is to only take one picture to capture the license plate, so as to minimize capture time and power consumption.

\subsubsection{License Plate Detection}
Once the image has been captured, the Raspberry Pi will then focus on detecting the license plate in the image and cropping the image to only include the license plate. This will be done in order to minimize the size of the transmission and the power required for that transmission. In order to detect the location of the license plate within the larger image, a detection algorithm needs to be applied.

@@

\subsection{Central Base Station}
The central base station will be the point of contact between the sensor network and the server. The data gathered by the Arduino Fio and Raspberry Pi sensors will be routed to the base station via XBee Pro radios. The base station, which will itself be a Raspberry Pi, will forward the data to the ACMx server using HTTP requests. Forwarding data is the main function of the base station. The base station will run the Raspbian operating system \cite{raspbian}, a lightweight version of Linux. Raspbian is optimized for the Raspberry Pi, so writing shell scripts that will take care of forwarding the data via HTTP to the server will be an easily achievable task. A second function of the base station will be to take periodic overhead photos of the parking lots to help reconcile the sensed data with the actual state of the lots. System administrators will be able to look at the photos to see if the number of cars reported in the lot by the sensors is correct, and fix any errors. See section 2.6 for more detailed information about the error correction functionality of the web application.

\subsection{Server Processing}
Once an image has been captured by an Acquisition Raspberry Pi it is transmitted via the XBee antenna to the base station Raspberry Pi where it is uploaded online via an Ethernet hardwire connection. The REST route that the image is posted serves several purposes. First, it authenticates the sender by checking for a username and password. The script then timestamps the image and saves it to a directory on the server not directly accessible from the web. Lastly, the script calls a function to invoke two different automatic license plate recognition (ALPR) programs and store the resulting character extraction to a MySQL database.

\subsubsection{ALPR Literature Survey}
License plate extraction algorithms have been developed, implemented, and critiqued in the academic community. For use in our project, we needed to find an implemented ALPR algorithm capable of running in a Linux environment (on the server) or a cloud service that would allow for reliable character recognition from license images.

@@

\subsubsection{ALPR Industry Survey}
Many ALPR systems exist today for commercial and government purposes. Uses can range from cross-referencing address information with the DMV to bill users of toll roads to monitoring roadways for stolen cars or even measuring car speeds. Our team was able to contact two manufacturers of ALPR systems to learn more about their use in industry: Q-Free ASA and The 3M Company.

@@

\subsubsection{Selection of ALPR Programs}
Our literature and industry surveys left us with three viable options for license plate recognition: OpenALPR, JavaANPR, and Q-Free's Intrada ALPR. Of those three, only OpenALPR was ready to be integrated into our network. Intrada ALPR is a commercial service, so our ability to use it was dependent on Q-Free granting an educational use license to us for the semester. Lastly, JavaANPR would need to be modified to detect and recognize North American plates and fonts. JavaANPR also lacks additional information that both OpenALPR and Intrada ALPR provide such as execution time and confidence.

@@

\subsubsection{Test Data Collection}
??? WHERE TO DISCUSS ACTUAL COLLECTION OF TEST DATA???

\subsubsection{ALPR-Project Integration}
Both OpenALPR and Intrada ALPR had to be integrated into our web application so they would run automatically without the need for human intervention. OpenALPR, because it is not a cloud service, needed to be installed locally on the ACMx server. The Intrada ALPR was much simpler because we were only interacting with the API.

\emph{A. OpenALPR}
As stated in ??? LITERATURE SURVEY REFERENCE ???, OpenALPR is built on top of OpenCV, a computer vision library, and Tesseract OCR, an OCR engine. Tesseract OCR had additional dependencies that needed to be installed before it would compile.

@@

\emph{B. Intrada ALPR}
Intrada ALPR uses the SOAP protocol for exchanging information. To create SOAP requests, we used the \verb+SoapClient+ class available in PHP to create, send, and receive the output of our request.

@@

\subsubsection{Evaluation Results}

\subsubsection{Proposal part}
Once an image has been determined to contain a license plate, it will be transmitted from the Acquisition Raspberry Pi to a server online via the base station Raspberry Pi. The server will then be responsible for using recognition software technology to extract the digits of the license plate from the image. Upon successful completion, the textual representation of the license plate will be stored in a database residing on the server to be later integrated into the front-facing web application.

@@

\subsubsection{Considerations for ALPR Software}
For the scope of this project, three ALPR solutions will be evaluated to determine which is the most suitable for our purposes. An ideal ALPR software needs to be currently maintained and capable of reading a license plate if it is skew in an image, taken in poor lighting conditions, and taken with low resolution.

@@

\subsubsection{Collection of Test Data}
Since two of the three proposed ALPR softwares do not require connecting to an external server for computation, it may be necessary to provide training data to improve the accuracy of the system. This would be in addition to the training data that comes with the libraries.

@@

\subsubsection{Interface with Base Station Raspberry Pi}
The recognition and extraction of license plate characters will not directly interface with the Arduino Fio or Acquisition Raspberry Pi that takes the images of automobiles. Instead, it is assumed all communications will come through the base station Raspberry Pi, and that the base station Raspberry Pi will upload received images to the ACMx Linux server (See section 2.6.1 about the HTTP interface).

@@

\subsection{Web Application}
As mentioned in section 1.2, the ACMx group has already created a web application that will display the data collected from the sensors in the system. The site is currently accessible online at \url{http://acmxlabs.org/parking/}. Since the current site is essentially just a shell with no data, one main goal of this project is to make the main pages of the site fully functional. Another main goal is to create an administrator side to the site, where data can be viewed and updated by site administrators. The main focus of this subsystem will be to provide interfaces for both general users and administrators that make the data we collect both useful and easy to access. Since the ACMx team already has some protocols in place for collecting and displaying the data from the magnetometer Arduino Fios, the ACMx team will continue development on this interface, and our group will focus on other parts of the application, as described below. The web application itself will be written with PHP on the back end and HTML5/CSS3/JavaScript on the front end. The following subsections describe the various pieces of the site that we aim to complete during this project.

\subsubsection{HTTP Interface}
The base station Raspberry Pi will need some way to communicate its data with the web application/MySQL database. The simplest way to meet this need is to create an HTTP interface on the server. We will need this interface to handle requests from the front end of the web application anyway, and so it makes sense to also allow the base station to communicate with our server through HTTP requests. We will create a REST-ful HTTP interface that corresponds closely to the database schema and the front-end of the webpage, and the base station will send all its data to the application via the same interface. For example, if an image of a license plate is detected, the base station would send an HTTP POST request to 'acmxlabs.org/parking/licenseImage' (actual urls may change when we start designing the interface), and the server would receive the request and send the image to the ALPR software, as described in section 2.5. When the web application needs to get the data associated with a license plate, it will send an HTTP GET request to 'acmxlabs.org/parking/licensePlate/123ABC'.

\subsubsection{Viewing License Plate Data}
As mentioned in section 2.5, the license plate images will be translated from an image into a string of plain text, and stored in the MySQL database on the ACMx server. One of the main functions of the web interface will be to display this data to administrators. The page that displays the license plate data will have a simple interface which will allow administrators to filter the data by date/time, lot, and license plate number. For example, an administrator should be able to type in a specific license plate number and see all the dates/times that plate has been seen, and in which lot. Alternatively, an administrator will be able to enter a date range and lot(s) and see all the license plates that entered/exited the lot(s) during that date range. For now we are only interested in a proof-of-concept type interface that shows we have the capability to display the collected plate data in a useful format; in the future it could be incredibly useful to cross reference our data with the campus parking department's database to check if a car has entered a lot without a permit.

\subsubsection{Validating and Adjusting Lot Capacity Data}
We expect that our first deployment of this system may not be 100\% accurate at detecting all vehicles that enter and exit lots. Therefore, as mentioned in section 2.4, we will be collecting periodic overhead images from a camera mounted on the base station Raspberry Pi. These images will serve as a visual representation of how many cars are actually in the parking lot at the time the image was taken. Administrators should be able to periodically compare this image to the collected data from the sensor network to make sure the numbers being computed by the network accurately represent the number of cars in the lot. The web interface will allow administrators to pull up the image for any lot with an overhead camera and see the numbers for that lot right next to the image. If any discrepancies are found, the administrator should be able to overwrite the count in the database to reflect reality. This interface will be extremely useful in helping to calibrate the system. For example, if the sensors are consistently reporting less cars in the lot than the image shows, we can fine-tune the collection process to make sure fewer cars slip through unnoticed. Future work in this area will include an automated version of this process, where a computer program will compare the image to the sensed data and make any necessary corrections.

\subsubsection{User Accounts}
As the site currently stands, there is no way to restrict certain data to administrators. We would like to create a simple user log-in system that allows general users to view the main parts of the site (maps of lots, state of each lot, stats and trends) without having to log in, and only allows access to the administrator side of the site (2.6.1 and 2.6.2, among other parts) if the user has a valid administrator username and password. This part of the project will also include an administrator interface that allows top administrators to create, update, and delete other administrators.

\subsection{Deployment}
The system will be deployed at the CTLM Upper and Lower parking lots at CSM. These lots were chosen because of their accessible location, unobstructed visibility from a campus structure, and wide use. Both parking lots have one entryway, each of which will be equipped with an automobile detection subsystem. The junction between the two lots is also of interest, because we want to know when a car moves from the upper lot to the lower lot, and vice versa. The locations of the entrances and junction are shown in Figure \ref{fig:deployment}. The locations for the three sensor nodes benefit from having a clear view of the sky for increased photovoltaic efficiency.
\begin{figure}
\begin{center}
\includegraphics[width=5in]{deployment}
\end{center}
\caption{Deployment Location}
\label{fig:deployment}
\end{figure}

@@

\section{Summary}
This project extends the work done by ACMx to create the first comprehensive parking management system for the Colorado School of Mines. The proposed expansions cover interfacing with the existing automobile detection network, acquiring images of license plates, processing those images, and presenting the resulting data in a web application.

>>>>

\subsection{Introduction}
{\color{red}\textbf{NOT COMPLETE}}
The parking lots at the Colorado School of Mines (CSM) can be a source of frustration for students and faculty members. Because space on campus is limited, the lots are often unable to accommodate everyone who needs to use them. Students need to choose a lot before they go to class; however, knowing which lots have free spaces usually requires driving through the lots looking for a space. The extra time spent searching one or many lots can make students or faculty late for class. If campus members could find out which lots had available spaces before they arrived, much time and frustration could be saved. The goal of this project is to design and deploy a working parking lot monitoring system that will be the first step towards a better parking experience on the CSM campus. The system will keep track of both the number of vehicles in a parking lot and the license plate numbers of those vehicles. The information will be available online to system administrators and CSM campus members. There are two main parts to this project:

@@

\subsection{Related Work}
{\color{red}\textbf{NOT COMPLETE}}
The ACMx group at CSM has designed a system named SmartLots to track the number of vehicles in a parking lot. Their system is a wireless sensor network consisting of sensor nodes and a central base station. The sensor nodes are based on the Arduino Fio microcontroller platform equipped with triaxial magnetometers and XBee Pro radios. The base station will be a Raspberry Pi connected to the internet via Ethernet. The information collected by the sensor nodes is transmitted to the base station and forwarded to a server running a small web application. The system is described in \cite{stillwell2013} and \cite{parkingWiki}. \cite{stillwell2013} describes an implementation of a system to detect automobiles entering and exiting a parking lot using the Arduino Fio and the Raspberry Pi. This system uses the IEEE 802.15.4 communications standard to communicate automobile detection data from the sensor nodes to the base station. \cite{parkingWiki} describes the ongoing status of the ACMx project. At the time of writing this proposal, the ACMx team has created a website that will display the status of the CTLM upper and lower lots once the monitoring system has been deployed. \cite{parkingWiki} is updated periodically with new information about project progress. The project described in this proposal will augment and extend the ACMx project while collaborating closely with Stillwell (ACMx president and coauthor of \cite{stillwell2013}), with the goal of a real world deployment by May 2014.

\section{Proposed Work}
{\color{red}\textbf{NOT COMPLETE}}
\subsection{Overview}
The project we are proposing will be an extension of the ACMx SmartLots project. We will collaborate closely with Stillwell and the ACMx group to create and deploy the first working parking lot monitoring system on the CSM campus. Our system will consist of several components, each of which will be either an extension of a current SmartLots system or an entirely new subsystem that will be integrated into the existing system. Figure \ref{fig:system} shows the overall architecture of our system.

@@

\subsection{Automobile Detection}
{\color{red}\textbf{NOT COMPLETE}}
The automobile detection subsystem will provide a means for detecting ingress and egress of vehicles from a parking lot. This subsystem is to be placed on the side of the road next to each parking lot entrance and exit. Automobiles will be detected using a magnetometer which perceives the induced change in the local magnetic field as the metallic structure of the vehicle passes by, as described in \cite{stillwell2013}. The automobile detection subsystem will be based around the commercially available Arduino Fio 16-bit  platform which utilizes the ubiquitous Atmel ATMEGA328p microcontroller. When an automobile is detected by the Arduino Fio, a packet will be sent through the onboard XBee Pro radio to the central base station (described in section 2.4). The packet will  contain the direction of the passing vehicle. At the time of detection, a hardware interrupt will also be sent to the license plate recognition system to awaken it from sleep mode.

@@

\subsubsection{Tests and Analyses}
{\color{red}\textbf{NOT COMPLETE}}
Because the ACMx group has already written the necessary software and designed a working configuration for detecting vehicles with the Arduino Fios, the bulk of our work on the automobile detection subsystem will involve a variety of tests and analyses to ensure system and data integrity. Power consumption analyses will be conducted on the automobile detection and license plate image acquisition subsystem to identify power usage per main component (Figure~\ref{fig:autodetect}) while the mote is in different states, such as sleeping and detecting vehicles. Such an analysis will allow us to allocate how much time the mote is allowed to spend in each state and determine the required lithium polymer battery capacity.

@@

\subsection{License Plate Image Acquisition}
{\color{red}\textbf{NOT COMPLETE}}
Once the Acquisition Raspberry Pi receives the interrupt from the vehicle detection Arduino Fio, it will begin the process of obtaining a picture of the vehicle's license plate. This procedure will be separated into two separate sections: image acquisition and license plate detection.

\subsubsection{Image Acquisition}
{\color{red}\textbf{NOT COMPLETE}}
While the automobile detection subsystem correctly identifies when a vehicle enters the lot, the image acquisition subsystem will be responsible for determining when to capture a picture of that car in order to optimize the quality of the license plate image. The timing difference between when the Raspberry Pi receives the interrupt and when it actually captures the picture will initially be determined experimentally using the average speed at which cars enter the parking lot. As the project progresses, this timing will be fine-tuned in order to capture the optimal image every time. The goal of this subsystem is to only take one picture to capture the license plate, so as to minimize capture time and power consumption.

\subsubsection{License Plate Detection}
{\color{red}\textbf{NOT COMPLETE}}
Once the image has been captured, the Raspberry Pi will then focus on detecting the license plate in the image and cropping the image to only include the license plate. This will be done in order to minimize the size of the transmission and the power required for that transmission. In order to detect the location of the license plate within the larger image, a detection algorithm needs to be applied.

@@

\subsection{Central Base Station}
{\color{red}\textbf{NOT COMPLETE}}
The central base station will be the point of contact between the sensor network and the server. The data gathered by the Arduino Fio and Raspberry Pi sensors will be routed to the base station via XBee Pro radios. The base station, which will itself be a Raspberry Pi, will forward the data to the ACMx server using HTTP requests. Forwarding data is the main function of the base station. The base station will run the Raspbian operating system \cite{raspbian}, a lightweight version of Linux. Raspbian is optimized for the Raspberry Pi, so writing shell scripts that will take care of forwarding the data via HTTP to the server will be an easily achievable task. A second function of the base station will be to take periodic overhead photos of the parking lots to help reconcile the sensed data with the actual state of the lots. System administrators will be able to look at the photos to see if the number of cars reported in the lot by the sensors is correct, and fix any errors. See section 2.6 for more detailed information about the error correction functionality of the web application.

\subsection{Server Processing}
{\color{red}\textbf{NOT COMPLETE}}
Once an image has been captured by an Acquisition Raspberry Pi it is transmitted via the XBee radio to the base station Raspberry Pi where it is uploaded online via an Ethernet connection. The REST route that the image is posted serves several purposes. First, it authenticates the sender by checking for a username and password. The script then timestamps the image and saves it to a directory on the server not directly accessible from the web. Lastly, the script calls a function to invoke two different automatic license plate recognition (ALPR) programs and store the resulting character extraction to a MySQL database.

\subsubsection{ALPR Literature Survey}
{\color{red}\textbf{NOT COMPLETE}}
License plate extraction algorithms have been developed, implemented, and critiqued in the academic community. For use in our project, we needed to find an implemented ALPR algorithm capable of running in a Linux environment (on the server) or a cloud service that would allow for reliable character recognition from license images.

@@

\subsubsection{ALPR Industry Survey}
{\color{red}\textbf{NOT COMPLETE}}
Many ALPR systems exist today for commercial and government purposes. Uses can range from cross-referencing address information with the DMV to bill users of toll roads to monitoring roadways for stolen cars or even measuring car speeds. Our team was able to contact two manufacturers of ALPR systems to learn more about their use in industry: Q-Free ASA and The 3M Company.

@@

\subsubsection{Selection of ALPR Programs}
{\color{red}\textbf{NOT COMPLETE}}
Our literature and industry surveys left us with three viable options for license plate recognition: OpenALPR, JavaANPR, and Q-Free's Intrada ALPR. Of those three, only OpenALPR was ready to be integrated into our network. Intrada ALPR is a commercial service, so our ability to use it was dependent on Q-Free granting an educational use license to us for the semester. Lastly, JavaANPR would need to be modified to detect and recognize North American plates and fonts. JavaANPR also lacks additional information that both OpenALPR and Intrada ALPR provide such as execution time and confidence.

@@

\subsubsection{Test Data Collection}
{\color{red}\textbf{NOT COMPLETE}}
??? WHERE TO DISCUSS ACTUAL COLLECTION OF TEST DATA???

\subsubsection{ALPR-Project Integration}
{\color{red}\textbf{NOT COMPLETE}}
Both OpenALPR and Intrada ALPR had to be integrated into our web application so they would run automatically without the need for human intervention. OpenALPR, because it is not a cloud service, needed to be installed locally on the ACMx server. The Intrada ALPR was much simpler because we were only interacting with the API.

\emph{A. OpenALPR}
{\color{red}\textbf{NOT COMPLETE}}
As stated in ??? LITERATURE SURVEY REFERENCE ???, OpenALPR is built on top of OpenCV, a computer vision library, and Tesseract OCR, an OCR engine. Tesseract OCR had additional dependencies that needed to be installed before it would compile.

@@

\emph{B. Intrada ALPR}
{\color{red}\textbf{NOT COMPLETE}}
Intrada ALPR uses the SOAP protocol for exchanging information. To create SOAP requests, we used the \verb+SoapClient+ class available in PHP to create, send, and receive the output of our request.

@@

\subsubsection{Evaluation Results}
{\color{red}\textbf{NOT COMPLETE}}

\subsubsection{Proposal part}
{\color{red}\textbf{NOT COMPLETE}}
Once an image has been determined to contain a license plate, it will be transmitted from the Acquisition Raspberry Pi to a server online via the base station Raspberry Pi. The server will then be responsible for using recognition software technology to extract the digits of the license plate from the image. Upon successful completion, the textual representation of the license plate will be stored in a database residing on the server to be later integrated into the front-facing web application.

@@

\subsubsection{Considerations for ALPR Software}
{\color{red}\textbf{NOT COMPLETE}}
For the scope of this project, three ALPR solutions will be evaluated to determine which is the most suitable for our purposes. An ideal ALPR software needs to be currently maintained and capable of reading a license plate if it is skew in an image, taken in poor lighting conditions, and taken with low resolution.

@@

\subsubsection{Collection of Test Data}
{\color{red}\textbf{NOT COMPLETE}}
Since two of the three proposed ALPR softwares do not require connecting to an external server for computation, it may be necessary to provide training data to improve the accuracy of the system. This would be in addition to the training data that comes with the libraries.

@@

\subsubsection{Interface with Base Station Raspberry Pi}
{\color{red}\textbf{NOT COMPLETE}}
The recognition and extraction of license plate characters will not directly interface with the Arduino Fio or Acquisition Raspberry Pi that takes the images of automobiles. Instead, it is assumed all communications will come through the base station Raspberry Pi, and that the base station Raspberry Pi will upload received images to the ACMx Linux server (See section 2.6.1 about the HTTP interface).

@@

\subsection{Web Application}
{\color{red}\textbf{NOT COMPLETE}}
As mentioned in section 1.2, the ACMx group has already created a web application that will display the data collected from the sensors in the system. The site is currently accessible online at \url{http://acmxlabs.org/parking/}. Since the current site is essentially just a shell with no data, one main goal of this project is to make the main pages of the site fully functional. Another main goal is to create an administrator side to the site, where data can be viewed and updated by site administrators. The main focus of this subsystem will be to provide interfaces for both general users and administrators that make the data we collect both useful and easy to access. Since the ACMx team already has some protocols in place for collecting and displaying the data from the magnetometer Arduino Fios, the ACMx team will continue development on this interface, and our group will focus on other parts of the application, as described below. The web application itself will be written with PHP on the back end and HTML5/CSS3/JavaScript on the front end. The following subsections describe the various pieces of the site that we aim to complete during this project.

\subsubsection{HTTP Interface}
{\color{red}\textbf{NOT COMPLETE}}
The base station Raspberry Pi will need some way to communicate its data with the web application/MySQL database. The simplest way to meet this need is to create an HTTP interface on the server. We will need this interface to handle requests from the front end of the web application anyway, and so it makes sense to also allow the base station to communicate with our server through HTTP requests. We will create a REST-ful HTTP interface that corresponds closely to the database schema and the front-end of the webpage, and the base station will send all its data to the application via the same interface. For example, if an image of a license plate is detected, the base station would send an HTTP POST request to 'acmxlabs.org/parking/licenseImage' (actual urls may change when we start designing the interface), and the server would receive the request and send the image to the ALPR software, as described in section 2.5. When the web application needs to get the data associated with a license plate, it will send an HTTP GET request to 'acmxlabs.org/parking/licensePlate/123ABC'.

\subsubsection{Viewing License Plate Data}
{\color{red}\textbf{NOT COMPLETE}}
As mentioned in section 2.5, the license plate images will be translated from an image into a string of plain text, and stored in the MySQL database on the ACMx server. One of the main functions of the web interface will be to display this data to administrators. The page that displays the license plate data will have a simple interface which will allow administrators to filter the data by date/time, lot, and license plate number. For example, an administrator should be able to type in a specific license plate number and see all the dates/times that plate has been seen, and in which lot. Alternatively, an administrator will be able to enter a date range and lot(s) and see all the license plates that entered/exited the lot(s) during that date range. For now we are only interested in a proof-of-concept type interface that shows we have the capability to display the collected plate data in a useful format; in the future it could be incredibly useful to cross reference our data with the campus parking department's database to check if a car has entered a lot without a permit.

\subsubsection{Validating and Adjusting Lot Capacity Data}
{\color{red}\textbf{NOT COMPLETE}}
We expect that our first deployment of this system may not be 100\% accurate at detecting all vehicles that enter and exit lots. Therefore, as mentioned in section 2.4, we will be collecting periodic overhead images from a camera mounted on the base station Raspberry Pi. These images will serve as a visual representation of how many cars are actually in the parking lot at the time the image was taken. Administrators should be able to periodically compare this image to the collected data from the sensor network to make sure the numbers being computed by the network accurately represent the number of cars in the lot. The web interface will allow administrators to pull up the image for any lot with an overhead camera and see the numbers for that lot right next to the image. If any discrepancies are found, the administrator should be able to overwrite the count in the database to reflect reality. This interface will be extremely useful in helping to calibrate the system. For example, if the sensors are consistently reporting less cars in the lot than the image shows, we can fine-tune the collection process to make sure fewer cars slip through unnoticed. Future work in this area will include an automated version of this process, where a computer program will compare the image to the sensed data and make any necessary corrections.

\subsubsection{User Accounts}
{\color{red}\textbf{NOT COMPLETE}}
As the site currently stands, there is no way to restrict certain data to administrators. We would like to create a simple user log-in system that allows general users to view the main parts of the site (maps of lots, state of each lot, stats and trends) without having to log in, and only allows access to the administrator side of the site (2.6.1 and 2.6.2, among other parts) if the user has a valid administrator username and password. This part of the project will also include an administrator interface that allows top administrators to create, update, and delete other administrators.

\subsection{Deployment}
{\color{red}\textbf{NOT COMPLETE}}
The system will be deployed at the CTLM Upper and Lower parking lots at CSM. These lots were chosen because of their accessible location, unobstructed visibility from a campus structure, and wide use. Both parking lots have one entryway, each of which will be equipped with an automobile detection subsystem. The junction between the two lots is also of interest, because we want to know when a car moves from the upper lot to the lower lot, and vice versa. The locations of the entrances and junction are shown in Figure \ref{fig:deployment}. The locations for the three sensor nodes benefit from having a clear view of the sky for increased photovoltaic efficiency.
\begin{figure}
\begin{center}
\includegraphics[width=5in]{deployment}
\end{center}
\caption{Deployment Location}
\label{fig:deployment}
\end{figure}

@@

\section{Summary}
{\color{red}\textbf{NOT COMPLETE}}
This project extends the work done by ACMx to create the first comprehensive parking management system for the Colorado School of Mines. The proposed expansions cover interfacing with the existing automobile detection network, acquiring images of license plates, processing those images, and presenting the resulting data in a web application.
